---
title: "Keras_MNIST_AssignmentNo.2"
author: "Nitin Khandare"
date: "September 16, 2018"
output: html_document
---

### For this assignment use KERAS as your library in R and write your own deep learning architecture to classify MNIST data. Without worrying on Accuracy, please experiment with the architecture and add dropouts to avoid overfitting.


### GitHub Pack Setup
```{r}
#install.packages("devtools")
#devtools::install_github("rstudio/keras")
knitr::opts_chunk$set(echo = TRUE)
```

### Keras and Tesnsorflow setup with Cuda Envi.
```{r}
# library(keras)

#install.packages("tensorflow")
#install_keras()
#install_tensorflow()

#install_tensorflow(gpu=TRUE)
```

## load the TensorFLow Library
```{r}
library(tensorflow)
```

## loading keras library
```{r}
library(keras)
```

### loading the keras inbuilt mnist dataset
```{r}
mnist = dataset_mnist()
```

### separating train and test file
```{r}

train_x = mnist$train$x
train_y = mnist$train$y
test_x = mnist$test$x
test_y = mnist$test$y

#rm(data)
```



### Converting a 2D array into a 1D array for feeding into the MLP and normalising the matrix
```{r}
train_x = array(train_x, dim = c(dim(train_x)[1], prod(dim(train_x)[-1]))) / 255
test_x = array(test_x, dim = c(dim(test_x)[1], prod(dim(test_x)[-1]))) / 255
```



### Converting the target variable to once hot encoded vectors using keras inbuilt function
```{r}
train_y = to_categorical(train_y,10)
test_y = to_categorical(test_y,10)
```


### Defining a keras sequential model
```{r}
model = keras_model_sequential()
```


## Defining the model with 1 input layer[784 neurons], 1 hidden layer[784 neurons] with dropout rate 0.4 and 1 output layer[10 neurons]
## i.e number of digits from 0 to 9

```{r}
model %>% 
layer_dense(units = 784, input_shape = 784) %>% 
layer_dropout(rate=0.5)%>%
layer_activation(activation = 'relu') %>% 
layer_dense(units = 10) %>% 
layer_activation(activation = 'softmax')

```


### Compiling the defined model with metric = accuracy and optimiser as adam.
```{r}
model %>% compile(
loss = 'categorical_crossentropy',
optimizer = 'adam',
metrics = c('accuracy')
)
```


### Fitting the model on the training dataset
```{r}
model %>% fit(train_x, train_y, epochs = 10, batch_size = 128)
```


### Evaluating model on the cross validation dataset
```{r}
loss_and_metrics = model %>% evaluate(test_x, test_y, batch_size = 128)
```

## Check the Accuracy and Loss
```{r}
loss_and_metrics
```

